\class : Problem Set \psetnum

### 2022-04-25 531_stars/exam1/exam.tex
finish up first draft of exam

>>>>

\question{\textbf{Part d - Minimum white dwarf mass to produce diamonds}}

\question{Carbon requires a pressure of at least $\sim 10^{10} \unit{Pa}$ to form diamonds. Find the minimum mass a white dwarf would need to convert carbon to diamonds in its core (assuming $A = 0.77$, $B=1.05 \unit{m}{kg^{1/3}}$, $C=10/3$ and $G = 6.67 \times 10^{-11} \unit{m^3}{kg^{-1}}{s^2}$).\\

\noindent What does this imply for which sorts of white dwarfs could work for Prof.\ Eyemund? How would you answer change qualitatively if the professor could only inject carbon near the surface rather than at the centre?}
\answer{}

\question{\textbf{Extra Credit - The Verdict}}

\question{Craft a response to Prof.\ Eyemund summarising the situation. Bonus points will be awarded for each dreadful pun.}

\answer{
    The solution is left as an exercise for the reader.
}
